Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-07-22 paper.qmd
Tweak first para of intro

Dangerous and criminal driving are significant problems that take many forms [@simon1996; @corbett2003; @corbett2010].
Across Great Britain there were an estimated 1,711 fatalities resulting from a road traffic crash in 2022 and 135,480 causalities reported across all severities [@departmentfortransportReportedRoadCasualties2023].

>>>>

Dangerous and criminal driving are significant problems that take many forms [@simon1996; @corbett2003; @corbett2010].
There were 1,711 fatalities and 135,480 causalities across all severity categories (slight, serious fatal) in Britain resulting from car crashes and other road traffic collisions reported by the police in 2022  [@departmentfortransportReportedRoadCasualties2023].
This is just the tip of the iceberg of road traffic incidents, with many more near misses and minor incidents going unreported.
